Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-10 ind_files/99_Appendix_A.tex
Add section on stochastic trait freq dynamics
Remove unneccessary math technicalities

\section*{Appendix A: From It\^{o} to Fokker-Planck}\label{sec_Ito_to_FPE}

@@

Consider a one-dimensional real It\^{o} process given by $dX_t = \mu(X_t,t)dt + \sigma(X_t,t)dB_t$ on a filtered probability space $\Omega \subseteq \mathbb{R}$ with probability measure $\mathbb{P}$ such that $\mathbb{P}(\cdot) \equiv 0$ on $\partial \Omega$ and $\mathbb{P} \ll m$, where $m$ is the Lebesgue measure. The latter requirement allows us to use the Radon-Nikodym theorem to write $\int \ \cdot \ d\mathbb{P} = \int \ \cdot \ P(x,t)dx$, where $P(x,t)$ is a `probability density function' defined at every point in $\Omega \times [0,\infty)$. Now, Let $f:\mathbb{R}\to\mathbb{R}$ be an arbitrary $C^2(\mathbb{R})$ function. By It\^{o}'s lemma, we have:
    df(X_t) = f'dX_t + \frac{1}{2}f''d\langle X\rangle_t
where $\langle \cdot \rangle$ denotes the quadratic variation. For $dX_t = \mu dt + \sigma dB_t$, it is clear that $d\langle X\rangle_t = \sigma^2d\langle B\rangle_t = \sigma^2dt$, and thus, we obtain:

@@

Since the Brownian motion is a martingale, as long as $X_t$ and $\sigma(X_t,t)$ are reasonably `nice'\footnote{We require $\sigma(X_t,t)f'(X_t) \in \mathcal{L}^*(B)$, which is a highly technical condition. Since existence/uniqueness of solutions for the SDE already requires Lipschitz continuity of $\sigma(X_t,t)$, this seems like a reasonable assumption to make.}, the stochastic integral in the second term of the RHS of \eqref{eq_expectation_Ito} will be a continuous $L^2(\mathbb{P})$ martingale starting at the origin, and its expectation will therefore be 0. Using the definition of the expectation value, we are thus left with:

>>>>

@@

Consider a one-dimensional real It\^{o} process given by $dX_t = \mu(X_t,t)dt + \sigma(X_t,t)dB_t$ on a filtered probability space $\Omega \subseteq \mathbb{R}$ that admits a probability density function $P(x,t)$ on $\Omega \times [0,\infty)$. Let $f:\mathbb{R}\to\mathbb{R}$ be an arbitrary $C^2(\mathbb{R})$ function. By It\^{o}'s formula, we have:

@@

Since the Brownian motion is a martingale, as long as $X_t$ and $\sigma(X_t,t)$ are reasonably `nice', the stochastic integral in the second term of the RHS of \eqref{eq_expectation_Ito} will be a continuous $L^2(\mathbb{P})$ martingale starting at the origin, and its expectation will therefore be 0. Using the definition of the expectation value, we are thus left with:
